Comments on Latent Ranking

### 2020-09-03 output_scripts/aug_updates.Rmd
removing some old material

```{r further checking permutation}
orig_stan_data <- prepareDataStan(current_cohort = 1)
permute_stan_data <- prepareData_permute_Stan(current_cohort = 1)
# now all pairs have an interaction

@@

```{r}
real_cleaned <- cleanData(full_data[[cohort_names[current_cohort]]])

permuted <- permute_raw(current_cohort)
permuted_cleaned <- cleanData(permuted)

permuted_cleaned$N_count - real_cleaned$N_count
# these look different which is good

return_df <- cleanObservationPeriod(current_cohort,
                                    full_data[[cohort_names[current_cohort]]],
                                    real_cleaned)

per_return_df <- cleanObservationPeriod(current_cohort,permuted,permuted_cleaned)

return_df$initiator - per_return_df$initiator
# so this is the issue then possibly

>>>>

```{r further checking permutation, include=FALSE, eval=FALSE}
orig_stan_data <- prepareDataStan(current_cohort = 1)
permute_stan_data <- prepareData_permute_Stan(current_cohort = 1)
# now all pairs have an interaction

@@

Then we want to check these fits and compare them.
